Motional Ground-State Cooling Outside the Lamb-Dicke Regime

### 2017-07-09 paper.tex
State detection note

Our experiment begins by loading a single sodium atom into an optical tweezer from a MOT
for $250$ ms~\cite{Hutzler2017-LightShifts} and repeats at $2.5$ Hz.
The tweezer is created by focusing a $700$nm laser beam through an NA=$0.55$ objective to
a beam waist of $0.7$ $\mu$m\fxnote{?}.
With $45$mW of tweezer power, the trapping frequencies are
$\{\omega_1,\omega_2,\omega_3\}/2\pi = \{69(1), 430(4), 590(5)\}\ \text{\text{kHz}}$.
Upon loading, an image is taken for $1.5$ms to determine its success.
The same imaging light is used for polarization gradient cooling (PGC) and
reduces the temperature of the single atom to $70$ $\mu$K,
which corresponds to an initial motional state along the three different axes of
$\{\bar n_1, \bar n_2, \bar n_3\}=\{21(2),\, 3.4(2),\, 2.5(2)\}$ (initial $P_0=0.3\%$) in the trap.

>>>>

Our experiment begins by loading a single sodium atom into an optical tweezer from a MOT
for $250$ ms~\cite{Hutzler2017-LightShifts} and repeats at $2.5$ Hz.
The tweezer is created by focusing a $700$nm laser beam through an NA=$0.55$ objective to
a beam waist of $0.7$ $\mu$m\fxnote{?}.
With $45$mW of tweezer power, the trapping frequencies are
$\{\omega_1,\omega_2,\omega_3\}/2\pi = \{69(1), 430(4), 590(5)\}\ \text{\text{kHz}}$.
Upon loading, an image is taken for $1.5$ms to determine its success.
The same imaging light is used for polarization gradient cooling (PGC) and
reduces the temperature of the single atom to $70$ $\mu$K,
which corresponds to an initial motional state along the three different axes of
$\{\bar n_1, \bar n_2, \bar n_3\}=\{21(2),\, 3.4(2),\, 2.5(2)\}$ (initial $P_0=0.3\%$) in the trap.
A beam with $\sigma^-$-polarization is used to optical pump the atom into
the $|F=2, m_F=-2\rangle$ stretch state.
The hyperfine state detection is done by pushing out atoms in the stretch state with a strong
beam on resonance with the $|F=2, m_F=-2\rangle$ to $|F'=3, m_{F'}=-3\rangle$ transition before
taking the second image.
The state preparation and detection have a combined fidelity of larger than $99$\%.
